Analysis plan

### 2023-09-25 04. Analysis/scripts/04-02-abstract.Rmd
Update 04-02-abstract.Rmd
Adding some statistics for leave

@@

```{r}
d <- 
  d %>% 
  mutate(across(
    .cols = c(daily_status_reporting_to_job_site,daily_status_teleworking),
    .fns = list(ppp = ~./prep_val_01,pm = ~./params$observation_window_length_months),
    .names = "{col}_{fn}"
  ))
```

@@

```{r}
d %>% 
  group_by(.cluster_5) %>% 
  skim(daily_status_reporting_to_job_site,
       daily_status_reporting_to_job_site_observation_prop,
       daily_status_reporting_to_job_site_working_prop,
       daily_status_reporting_to_job_site_ppp,
       daily_status_reporting_to_job_site_pm,
       daily_status_teleworking,
       daily_status_teleworking_observation_prop,
       daily_status_teleworking_working_prop,
       daily_status_teleworking_ppp,
       daily_status_teleworking_pm,
       days_colocated_1,
       days_colocated_1_observation_prop,
       days_colocated_supervisor,
       days_colocated_supervisor_observation_prop,
       days_colocated_team,
       days_colocated_team_observation_prop,
       days_telework_team,
       days_telework_team_observation_prop,
       working_days,
       team_size_mode)
```

@@

>>>>

## Percent of GSA employees by office

```{r}
prep_d_01 <- 
  d %>%
  group_by(gsa_sso) %>% 
  count() %>% 
  ungroup()

@@

```{r}
d <- 
  d %>% 
  mutate(across(
    .cols = c(daily_status_reporting_to_job_site,daily_status_teleworking, daily_status_leave),
    .fns = list(ppp = ~./prep_val_01,pm = ~./params$observation_window_length_months),
    .names = "{col}_{fn}"
  ))
```

@@

```{r}
d %>% 
  group_by(.cluster_5) %>% 
  skim(daily_status_reporting_to_job_site,
       daily_status_reporting_to_job_site_observation_prop,
       daily_status_reporting_to_job_site_working_prop,
       daily_status_reporting_to_job_site_ppp,
       daily_status_reporting_to_job_site_pm,
       daily_status_teleworking,
       daily_status_teleworking_observation_prop,
       daily_status_teleworking_working_prop,
       daily_status_teleworking_ppp,
       daily_status_teleworking_pm,
       daily_status_leave,
       daily_status_leave_pm,
       daily_status_leave_ppp,
       days_colocated_1,
       days_colocated_1_observation_prop,
       days_colocated_supervisor,
       days_colocated_supervisor_observation_prop,
       days_colocated_team,
       days_colocated_team_observation_prop,
       days_telework_team,
       days_telework_team_observation_prop,
       working_days,
       team_size_mode)
```

@@

# Work and leave ppp

```{r}
prep_d_06 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  summarise(
    across(
      .cols = ends_with("_ppp"),
      .fns = mean
    )
  ) %>% 
  pivot_longer(cols = -.cluster_5) %>% 
  mutate(
    name = str_remove(name,"daily_status_"),
    name = str_remove(name,"_ppp"),
    name = str_replace_all(name,"_", " "),
    name = str_to_sentence(name),
    name = str_wrap(name, width = 15)
  )

prep_d_06
```

```{r}
p_3 <- 
  prep_d_06 %>% 
  ggplot(aes(x = .cluster_5, y = value, fill = name)) +
  geom_bar(stat = "identity") +
  labs(title = "Work and leave per pay period") +
  ylab("Days per pay period") +
  scale_y_continuous(labels = scales::comma) +
  oescolorrrs::scale_fill_oes() +
  oescolorrrs::scale_color_oes() +
  theme_light() +
  theme(
    legend.position = "right",
    legend.title = element_blank(),
    plot.title = element_text(hjust = 0.5,
                              size = 13),
    axis.title.y = element_text(size = 8),
    axis.title.x = element_blank()
    )

p_3
```

```{r}
file_name <- "abstract_3.png"
fp <- file.path(params$google_drive_home,"04. Analysis", "output", "png",file_name)
```

```{r}
ggsave(filename = fp, plot = p_3, width = 6, height = 3, units = "in")
```
